---
title: "2020FebruaryAustralia_report"
author: "Tim C."
date: "05/18/2020"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---
```{r, echo=F, warning = F, message=F}
# load packages
library(tidyverse)
library(ggmap)
library(memoise)
library(lubridate)
library(cowplot)
library(pals)
library(grid)
library(gridExtra)
library(scales)
library(kableExtra)
library(leaflet)
library(htmlwidgets)
library(htmltools)

#setting working directory
knitr::opts_knit$set(root.dir = '..')
```

```{r, echo=F, warning = F, message=F}
# load fulcrum data
load('data/fulcrum/2020FebruaryAustralia_fulcrum_v2.Rda')

fulcrum_dat <- `2020FebruaryAustralia_fulcrum_v2`
rm(`2020FebruaryAustralia_fulcrum_v2`)
#################################################
### set color palettes                        ###
#################################################
species_palette <- c("C. elegans" = "#BE0032", #7
                     "C. oiwi" =  "#875692", #4 
                     "C. tribulationis" = "#F38400", #5 
                     "Panagrolaimus sp." = "#C2B280", #8
                     "Oscheius sp." = "#F3C300", #3
                     "C. briggsae" = "#A1CAF1", #6 
                     "Other PCR +" = "#008856", #10
                     "PCR -" = "#848482", #9
                     "Not genotyped" = "#F2F3F4", #1
                     "Tracks only" = "#b3b3b3", #manual
                     "No Nematode" = "#222222")  #2

island_palette <- c("Kauai" = "#E69F00",
                    "Oahu" = "#56B4E9",
                    "Molokai" = "#009E73",
                    "Maui" = "#F0E442",
                    "Big Island" = "#D55E00")

#################################################
### Define Functions                          ###
#################################################
# function used in map_overview to set as numeric
as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}

# Function for setting islands 
filter_box <- function(longitude, latitude, coords) {
  between(longitude, coords[1], coords[3]) &
    between(latitude, coords[2], coords[4]) &
    !is.na(longitude)
}

# make function to catch emptys
is.empty <- function(x, mode=NULL){
  if (is.null(mode)) mode <- class(x)
  identical(vector(mode,1),c(x,vector(class(x),1)))
}

# coordinates for islands. Note need to comment out islands not collected from in this list
islands = list(  "Kauai" = c(-159.830818,21.750571,-159.230003,22.350076),
  "Oahu" = c(-158.323116,21.112767,-157.623081,21.814254),
  "Molokai" = c(-157.3515,20.793,-156.6515,21.4956),
  "Maui" = c(-156.745977,20.405495,-155.942774,21.207099),
  "Big Island" = c(-156.3651,18.8049,-154.765,20.4064)
)

#gtmap function for map_overview function
gtmap <- function(loc) {
  get_map(location = loc,
          maptype = "terrain-background",
          source = "stamen",
          scale = "auto")
}
mget_map <- memoise(gtmap)

# NOTE: You must configure set_islands to what was sampled in this project for this script to work (see lines150 - 163).
# Overview map plotting function
map_overview <- function(F, label, cso, geoms, face = "plain") {
  island_set = lapply(names(islands), function(i) {
    
    l_position = "none"
    island_size = 2
    imap <- cso %>% dplyr::filter(collection_island == i)
    rects = element_blank()
    map = mget_map(islands[[i]])
    
    # Calculate scalebar
    bb <- attr(map,"bb")
    sbar <- data.frame(lon.start = c(bb$ll.lon + 0.1*(bb$ur.lon - bb$ll.lon)),
                       lon.end = c(bb$ll.lon + 0.25*(bb$ur.lon - bb$ll.lon)),
                       lat.start = c(bb$ll.lat + 0.1*(bb$ur.lat - bb$ll.lat)),
                       lat.end = c(bb$ll.lat + 0.1*(bb$ur.lat - bb$ll.lat)))
    
    sbar$distance <- geosphere::distVincentyEllipsoid(c(sbar$lon.start,sbar$lat.start),
                                                      c(sbar$lon.end,sbar$lat.end))
    
    scalebar.length <- 20
    sbar$lon.end <- sbar$lon.start +
      ((sbar$lon.end-sbar$lon.start)/sbar$distance)*scalebar.length*1000
    ptspermm <- 2.83464567
    
    base_map <- ggplot(imap) +
      ggmap::inset_ggmap(map) +
      #rects +
      geoms +
      theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(),
            axis.ticks.y = element_blank(), axis.text.y = element_blank(),
            axis.title.x = element_blank(), axis.title.y = element_blank(),
            panel.background = element_blank(),
            panel.spacing = unit(c(0,0,0,0), "lines"),
            axis.line = element_blank(),
            plot.title = element_text(lineheight=.8, face="bold", vjust=1),
            plot.margin = unit(c(0,0,0,0), "lines"),
            panel.grid = element_blank(),
            panel.border = element_blank(),
            legend.position = l_position,
            legend.background = element_rect(fill="white"),
            legend.text=element_text(size=12, color = "black", face = face)) +
      coord_equal(ratio=1) +
      scale_x_continuous(limits = islands[[i]][c(1,3)], expand = c(0, 0)) +
      scale_y_continuous(limits = islands[[i]][c(2,4)], expand = c(0, 0)) +
      geom_segment(data = sbar,
                   aes(x = lon.start,
                       xend = lon.end,
                       y = lat.start,
                       yend = lat.end),
                   arrow=arrow(angle = 90, length = unit(0.1, "cm"),
                               ends = "both", type = "open")) +
      geom_text(data = sbar,
                aes(x = (lon.start + lon.end)/2,
                    y = lat.start + 0.025*(bb$ur.lat - bb$ll.lat),
                    label = paste(format(scalebar.length),
                                  'km')),
                hjust = 0.5,
                vjust = 0,
                size = 8/ptspermm)  +
      coord_map(projection = "mercator",
                xlim=c(bb$ll.lon, bb$ur.lon),
                ylim=c(bb$ll.lat, bb$ur.lat)) +
      scale_radius(range = c(island_size, island_size), guide = "none") #+
    #scale_shape_manual(values = shape)
    
    base_map
    
  })
  
  island_set[[6]] <- F
  
  without_label <- plot_grid(plotlist = island_set,
            labels = c("A - Kauai",
                       "B - O'ahu",
                       "C - Moloka'i",
                       "D - Maui",
                       "E - Island of Hawai'i",
                       "F", ""
            ),
            label_y = 0.98,
            hjust = 0,
            label_x = 0.06,
            align = "vh")
  
  cowplot::plot_grid(without_label, label, nrow = 2, rel_heights = c(1, .05))
}

# Map_collection function for reviewing collection locations
map_collection <- function(df, color_use) {
  
  icos <- iconList(
    red = makeIcon(
      iconUrl = paste0("https://storage.googleapis.com/andersenlab.org/img/red.svg"),
      iconWidth = 20, iconHeight = 20,
      popupAnchorX = 0.001, popupAnchorY = -20,
      iconAnchorX = 20/2, iconAnchorY = 20
    ),
    green = makeIcon(
      iconUrl = paste0("https://storage.googleapis.com/andersenlab.org/img/green.svg"),
      iconWidth = 10, iconHeight = 10,
      popupAnchorX = 0.001, popupAnchorY = -10,
      iconAnchorX = 10/2, iconAnchorY = 10
  )
)
  #df <- dplyr::filter(df, !is.na(df[[color_use]])) %>%
   # dplyr::mutate(substrate=ifelse(is.na(substrate), "", substrate)) %>%
    #dplyr::arrange(collection_lat_long_method)
  
  #print(df)
 
  
  attach(df)
  leaflet::leaflet(data = df, width = "100%", options = list(zoomControl = T)) %>% 
    leaflet::addTiles( 
      paste0( 
        "https://stamen-tiles-{s}.a.ssl.fastly.net/terrain/{z}/{x}/{y}.png",
        jsonlite::read_json("data/thunderforest.json")$key)  
    ) %>%
    leaflet::addMarkers(~collection_longitude,
                        ~collection_latitude,
                        popup = glue::glue("<h2>{collection_id}</h2><hr />
                                           <strong>trail:</strong> {collection_trail}<br />
                                           <strong>collection uplaoded by:</strong> {collection_by}<br />
                                           <strong>latitidue, longitude:</strong> {format(round(collection_latitude, 6), nsmall = 6)}, {format(round(collection_longitude, 6), nsmall = 6)}<br />
                                           <strong>postion method used:</strong> {collection_lat_long_method}<br />
                                           <strong>local time:</strong> {collection_local_time}<br />
                                           <strong>altitude:</strong> {altitude} meters<br />
                                           <strong>landscape:</strong> {landscape}<br /><br />"),
                        popupOptions(maxWidth = 500),
                        icon = icos[ df[[color_use]] ] )
  
  #htmlwidgets::saveWidget(m, tempfile(), selfcontained = FALSE)
  #webshot::webshot("temp.html", file = "map.png",
  #        cliprect = "viewport", vwidth = 1000, vheight = 1000)
}
```

### Personnel
```{r, echo=F, warning = F, message=F}
# pull names of personnel
collectors <- pull(fulcrum_dat%>%dplyr::distinct(collection_by)%>%dplyr::filter(!is.na(collection_by)))
isolators <- pull(fulcrum_dat%>%dplyr::distinct(isolation_by)%>%dplyr::filter(!is.na(isolation_by)))

# make personnel dataframe
personnel_collectors <- data.frame(collectors)
personnel_isolators <- data.frame(isolators)

# print nice tables 
knitr::kable(personnel_collectors)
knitr::kable(personnel_isolators)
```
<br>

### Collection Report
```{r, echo=F, warning = F, message=F}
# Find counts
collection_counts_1 <- fulcrum_dat %>%
  dplyr::distinct(collection_id, .keep_all = TRUE) %>%
  dplyr::mutate(`total number of distinct collections` = n()) %>%
  dplyr::filter(!is.na(collection_id)) %>%
  dplyr::mutate(`total number of distinct collections NAs removed` = n()) %>%
  dplyr::add_count(worms_on_sample) %>%
  dplyr::rename(worms_on_sample_counts = n) %>%
  dplyr::select(worms_on_sample, `total number of distinct collections`:worms_on_sample_counts) %>%
  dplyr::distinct(worms_on_sample, .keep_all = T)

# find more counts
`total number of distinct collections` <- dplyr::pull(collection_counts_1 %>% dplyr::distinct(`total number of distinct collections`))
`total number of distinct collections NAs removed` <- dplyr::pull(collection_counts_1 %>% dplyr::distinct(`total number of distinct collections NAs removed`))
`collections with nematodes` <- dplyr::pull(collection_counts_1 %>% dplyr::filter(worms_on_sample == "Yes") %>% dplyr::distinct(`worms_on_sample_counts`))
`collections with tracks only` <- ifelse(is.empty(dplyr::pull(collection_counts_1 %>%
                                                                dplyr::filter(worms_on_sample == "Tracks") %>%
                                                                dplyr::distinct(`worms_on_sample_counts`)), "integer") == TRUE, 0,
                                         dplyr::pull(collection_counts_1 %>%
                                                                dplyr::filter(worms_on_sample == "Tracks") %>%
                                                                dplyr::distinct(`worms_on_sample_counts`))) 
`collections without nematodes`<- dplyr::pull(collection_counts_1 %>% dplyr::filter(worms_on_sample == "No") %>% dplyr::distinct(`worms_on_sample_counts`))
`collections without paired isolation data`<- collection_counts_1 %>%
  dplyr::filter(worms_on_sample == "?" | is.na(worms_on_sample)) %>%
  dplyr::mutate(na_count = sum(`worms_on_sample_counts`)) %>%
  distinct(na_count) %>%
  pull(na_count)
`rows with NA for colleciton id` <- ifelse(is.empty(dplyr::pull(fulcrum_dat %>%
                                                                         dplyr::filter(is.na(collection_id)) %>%
                                                                         dplyr::mutate(n = n()) %>%
                                                                         dplyr::distinct(n)), "integer") == TRUE, 0,
                                                  dplyr::pull(fulcrum_dat %>%
                                                                dplyr::filter(is.na(collection_id)) %>%
                                                                dplyr::mutate(n = n()) %>%
                                                                dplyr::distinct(n)))

# find duplicate c_labels
`collections with duplicated ids` <-  fulcrum_dat %>%
  dplyr::filter(!is.na(collection_id)) %>%
  dplyr::distinct(collection_id, isolation_datetime_UTC, .keep_all = T) %>%
  dplyr::group_by(collection_id) %>%
  dplyr::mutate(n = n()) %>% 
  dplyr::ungroup() %>%
  dplyr::mutate(duplicated = ifelse(n > 1, 1, 0)) %>%
  dplyr::mutate(num_duplicated = sum(duplicated)) %>%
  dplyr::distinct(num_duplicated) %>%
  dplyr::pull(num_duplicated)

# Find counts for location and altitude methods
collection_counts_2 <-  fulcrum_dat %>%
  dplyr::filter(!is.na(collection_id)) %>%
  dplyr::distinct(collection_id, .keep_all =T) %>%
  dplyr::add_count(collection_lat_long_method) %>%
  dplyr::rename(`location method n` = n) %>%
  dplyr::add_count(altitude_method) %>%
  dplyr::rename(`altitude method n` = n) %>%
  dplyr::select(collection_lat_long_method, `location method n`, altitude_method, `altitude method n`)

`collections with location method 'photo'` <- collection_counts_2 %>% dplyr::filter(collection_lat_long_method == "photo") %>%
  dplyr::distinct(`location method n`) %>% pull(unique(`location method n`))
`collection percentage with loc method 'photo'` <- (`collections with location method 'photo'` / `total number of distinct collections NAs removed`)

`collections with location method 'fulcrum'` <- collection_counts_2 %>% dplyr::filter(collection_lat_long_method == "fulcrum") %>%
  dplyr::distinct(`location method n`) %>% pull(unique(`location method n`))
`collection percentage with loc method 'fulcrum'` <- (`collections with location method 'fulcrum'` / `total number of distinct collections NAs removed`)

`collections with altitude method 'photo'` <- ifelse(is.empty(collection_counts_2 %>% 
                                                                  dplyr::filter(altitude_method == "photo") %>%
                                                                  dplyr::distinct(`altitude method n`) %>%
                                                                  dplyr::pull(unique(`altitude method n`))), 0,
                                                       collection_counts_2 %>% 
                                                                  dplyr::filter(altitude_method == "photo") %>%
                                                                  dplyr::distinct(`altitude method n`) %>%
                                                                  dplyr::pull(unique(`altitude method n`)))

`collections with altitude method 'geonames'` <-  ifelse(is.empty(collection_counts_2 %>% 
                                                                  dplyr::filter(altitude_method == "geonames") %>%
                                                                  dplyr::distinct(`altitude method n`) %>%
                                                                  dplyr::pull(unique(`altitude method n`))), 0,
                                                       collection_counts_2 %>% 
                                                                  dplyr::filter(altitude_method == "geonames") %>%
                                                                  dplyr::distinct(`altitude method n`) %>%
                                                                  dplyr::pull(unique(`altitude method n`)))

`collections with altitude method 'fulcrum'` <- ifelse(is.empty(collection_counts_2 %>% 
                                                                  dplyr::filter(altitude_method == "fulcrum") %>%
                                                                  dplyr::distinct(`altitude method n`) %>%
                                                                  dplyr::pull(unique(`altitude method n`))), 0,
                                                       collection_counts_2 %>% 
                                                                  dplyr::filter(altitude_method == "fulcrum") %>%
                                                                  dplyr::distinct(`altitude method n`) %>%
                                                                  dplyr::pull(unique(`altitude method n`)))

`collection percentage with altitude method 'photo'` <- (`collections with altitude method 'photo'` / `total number of distinct collections NAs removed`)

`collection percentage with altitude method 'geonames'` <- (`collections with altitude method 'geonames'` / `total number of distinct collections NAs removed`)

`collection percentage with altitude method 'fulcrum'` <- (`collections with altitude method 'fulcrum'` / `total number of distinct collections NAs removed`)

# build data frame to display
collection_counts <- tibble(`total number of distinct collections`,
                            `total number of distinct collections NAs removed`,
                            `collections with nematodes`,
                            `collections with tracks only`,
                            `collections without nematodes`) %>%
  dplyr::mutate(`collection percentage with nematodes` = (`collections with nematodes`/`total number of distinct collections NAs removed`),
                `collection percentage with tracks only` = (`collections with tracks only`/`total number of distinct collections NAs removed`),
                `collection percentage with no worms` = (`collections without nematodes`/`total number of distinct collections NAs removed`)) %>%
  dplyr::bind_cols(list(`collections with duplicated ids`,
                   `rows with NA for colleciton id`,
                   `collections without paired isolation data`,
                   `collections with location method 'photo'`,
                   `collections with location method 'fulcrum'`,
                   `collection percentage with loc method 'photo'`,
                   `collection percentage with loc method 'fulcrum'`,
                   `collections with altitude method 'photo'`,
                   `collections with altitude method 'geonames'`,
                   `collections with altitude method 'fulcrum'`,
                   `collection percentage with altitude method 'photo'`,
                   `collection percentage with altitude method 'geonames'`,
                   `collection percentage with altitude method 'fulcrum'`)) %>%
  dplyr::rename(`collections with duplicated ids` = V1,
                   `rows with NA for colleciton id` = V2,
                   `collections without paired isolation data` = V3,
                   `collections with location method 'photo'` = V4,
                   `collections with location method 'fulcrum'` = V5,
                   `collection percentage with loc method 'photo'` = V6,
                   `collection percentage with loc method 'fulcrum'` = V7,
                   `collections with altitude method 'photo'` = V8,
                   `collections with altitude method 'geonames'` = V9,
                   `collections with altitude method 'fulcrum'` = V10,
                   `collection percentage with altitude method 'photo'` = V11,
                   `collection percentage with altitude method 'geonames'` = V12,
                   `collection percentage with altitude method 'fulcrum'` = V13) %>%
  tidyr::gather(`collection report`, value) %>%
  dplyr::mutate(value = as.numeric(value)) %>%
  # if percentage in type then display as percentage
  dplyr::mutate(value = ifelse(str_detect(`collection report`, pattern = "percentage"), percent(value, scale = 100, accuracy = .1, trim = T), as.integer(value)))

# make nice table
knitr::kable(collection_counts)
```

### Isolation Report
```{r, echo=F, warning = F, message=F}
# Find counts
isolation_counts1 <- fulcrum_dat %>%
 dplyr::distinct(isolation_id, .keep_all = T) %>%
  dplyr::mutate(`total number of distinct isolations` = n()) %>%
  dplyr::filter(!is.na(isolation_id)) %>%
  dplyr::mutate(`total number of distinct isolations NAs removed` = n())

`total number of distinct isolations` <- isolation_counts1 %>% dplyr::distinct(`total number of distinct isolations`) %>% pull(`total number of distinct isolations`)

`total number of distinct isolations NAs removed` <- isolation_counts1 %>% dplyr::distinct(`total number of distinct isolations NAs removed`) %>% pull(`total number of distinct isolations NAs removed`)

`average isolations per collection with worms` <- fulcrum_dat %>%
  dplyr::filter(!is.na(isolation_id), !is.na(collection_id)) %>%
  dplyr::group_by(collection_id) %>%
  dplyr::mutate(num_isolations_for_collection = n()) %>%
  dplyr::ungroup() %>%
  dplyr::distinct(collection_id, .keep_all = T) %>%
  dplyr::mutate(`average isolations per collection with worms` = mean(num_isolations_for_collection)) %>%
  dplyr::distinct(`average isolations per collection with worms`) %>%
  dplyr::pull(`average isolations per collection with worms`)

`isolations with duplicated ids` <- fulcrum_dat %>%
  add_count(isolation_id) %>%
  dplyr::filter(n > 1 & !is.na(isolation_id)) %>%
  dplyr::distinct(isolation_id) %>%
  dplyr::pull(isolation_id) %>%
  paste(., collapse = ",") %>%
  ifelse(. == "", return(0), .)
  
`isolations without paired collection data` <- fulcrum_dat %>%
  dplyr::filter(is.na(collection_id)) %>%
  dplyr::mutate(n = n()) %>%
  dplyr::distinct(isolation_id, .keep_all = T) %>%
  dplyr::mutate(isolation_unpaired_names = paste(.$isolation_id, collapse =",")) %>%
  dplyr::distinct(n, .keep_all = T) %>%
  dplyr::mutate(`isolations without paired collection data` = glue::glue('({.$n} plates) {.$isolation_unpaired_names}')) %>%
  dplyr::pull(`isolations without paired collection data`)
  
# find counts for genotypes
isolation_counts3 <- fulcrum_dat %>%
  dplyr::mutate(collection_type = ifelse(worms_on_sample %in% c("No", "?"), "No Nematode",
                                   ifelse(worms_on_sample == "Tracks", "Tracks only",
                                          ifelse(worms_on_sample == "Yes" & is.na(worms_on_sample), "Not genotyped",
                                                 ifelse(worms_on_sample == "Yes" & pcr_product_its2 == 0, "PCR -", species_id))))) %>%
  dplyr::select(isolation_id, collection_id, collection_type, collection_island, species_id, pcr_product_its2, worms_on_sample, collection_longitude, collection_latitude) %>%
  dplyr::filter(collection_type != "Tracks only", collection_type != "No Nematode") %>%
  dplyr::distinct(collection_id, isolation_id, .keep_all=T) %>% 
  dplyr::add_count(collection_type) %>%
  dplyr::arrange(collection_type) %>%
  dplyr::mutate(total = n()) %>%
  dplyr::distinct(collection_type, n) %>%
  dplyr::rename(`isolation report` = collection_type,
                value = n) %>%
  dplyr::mutate(value = as.character(value))
 
`Possible new Caenorhabditis sp. isolations` <- fulcrum_dat %>%
  dplyr::filter(possible_new_caeno_sp == 1) %>%
  dplyr::mutate(n = n()) %>%
  dplyr::distinct(n) %>%
  dplyr::pull(unique(n)) %>%
  ifelse(length(.) == 0, return(0), .)

`Isolations that need to be resequenced` <- fulcrum_dat %>%
  dplyr::filter(pcr_product_its2 == 1) %>%
  dplyr::filter(manual_blast_notes %in% c("Needs to be redone",
"no significant match; redo",
"short sequence region, though. redo?",
"only ~55% of the query matched, so maybe redo?",
"a few mismatches, redo?",                               
"only ~62% of the query matched, so maybe redo?", 
"Not high identity",       
"redo",                                                                                        
"But sequence may be bad") | (is.na(species_id)) | species_id %in% c("No significance", "No signficance", "No amplification", "uncultured soil fungus")) %>%
  dplyr::mutate(n = n()) %>%
  dplyr::distinct(n) %>%
  dplyr::pull(unique(n))

# add it all together
isolation_report <- tibble(`total number of distinct isolations`,
                          `total number of distinct isolations NAs removed`,
                          `average isolations per collection with worms`,
                          `isolations with duplicated ids`,
                          `isolations without paired collection data`,
                          #`Possible new Caenorhabditis sp. isolations`,
                          `Isolations that need to be resequenced`) %>%
   tidyr::gather(`isolation report`, value) %>%
  dplyr::full_join(isolation_counts3) %>%
  dplyr::mutate(value = as.character(value))

# make nice table
knitr::kable(isolation_report)
```

### Duplications Report
```{r, echo=F, warning = F, message=F}
##########################################################################
# part 1 find duplications in nematode nematode_field_sampling.csv     ###
##########################################################################
`duplication in nematode_field_sampling.csv` <- readr::read_csv("data/fulcrum/nematode_field_sampling.csv") %>%
  add_count(c_label) %>%
  dplyr::filter(n > 1)

n_duplicated_field_sampling <- `duplication in nematode_field_sampling.csv` %>%
  #conditional pipe to return NA if dataframe is empty and move on to count c_labels if not empty.
    {if (nrow(.) == 0) return(0) else (.) %>%
  dplyr::distinct(c_label) %>%
  dplyr::mutate(pull_n = n()) %>%
  dplyr::distinct(pull_n) %>%
  dplyr::pull(pull_n)
    }

knitr::kable(`duplication in nematode_field_sampling.csv`, caption = glue::glue("{n_duplicated_field_sampling} c_label(s) duplicated in nematode_field_sampling.csv")) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

#########################################################################
# part 2  find duplicate records in nematode_isolation.csv            ###
#########################################################################
`duplication in nematode_isolation.csv` <- readr::read_csv("data/fulcrum/nematode_isolation.csv") %>%
  add_count(fulcrum_id) %>%
  dplyr::rename(distinct_fulcrum_id_count = n) %>%
  add_count(c_label) %>%
  dplyr::rename(distinct_c_label_count = n)

# get count of duplicated isolation ids
n_duplicated_isolations <- `duplication in nematode_isolation.csv` %>%
  dplyr::filter(distinct_fulcrum_id_count > 1) %>%
  #conditional pipe to return NA if dataframe is empty and move on to count fulcrum_ids if not empty.
    {if (nrow(.) == 0) return(0) else (.) %>%
  dplyr::distinct(fulcrum_id) %>%
  dplyr::mutate(pull_n = n()) %>%
  dplyr::distinct(pull_n) %>%
  dplyr::pull(pull_n)
    }

`duplicated isolation ids in nematode_isolation.csv` <-  `duplication in nematode_isolation.csv` %>% dplyr::filter(distinct_fulcrum_id_count >1)
knitr::kable(`duplicated isolation ids in nematode_isolation.csv`, caption = glue::glue("{n_duplicated_isolations} isolation id(s) duplicated in nematode_isolation.csv")) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

# get count of multiple isolation ids for a single collection
n_multiple_isolations_for_collection <- `duplication in nematode_isolation.csv` %>%
  dplyr::filter(distinct_c_label_count > 1) %>%
  #conditional pipe to return NA if dataframe is empty and move on to count c_labels if not empty. Need (.) b/c you can't have . alone on the left side of a pipe!
    {if (nrow(.) == 0) return(0) else (.) %>%
  dplyr::distinct(c_label) %>%
  dplyr::mutate(pull_n = n()) %>%
  dplyr::distinct(pull_n) %>%
  dplyr::pull(pull_n)
    }
    
`duplicated isolations for same collection` <- `duplication in nematode_isolation.csv` %>% dplyr::filter(distinct_c_label_count >1)
knitr::kable(`duplicated isolations for same collection`, caption = glue::glue("{n_multiple_isolations_for_collection} collection(s) with duplicated isolations in nematode_isolation.csv")) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

#########################################################################
# part 3 find duplications in nematode isolation_s_labeled_plates.csv ###
#########################################################################
`duplication in nematode_isolation_s_labeled_plates.csv` <- readr::read_csv("data/fulcrum/nematode_isolation_s_labeled_plates.csv") %>%
  add_count(s_label) %>%
  dplyr::filter(n > 1)

# get count of duplicated isolations in nematode isolation_s_labeled_plates.csv
n_duplicated_isolations_s_labeled_plates <- `duplication in nematode_isolation_s_labeled_plates.csv` %>%
  #conditional pipe to return NA if dataframe is empty and move on to count s_labels if not empty. Need (.) b/c you can't have . alone on the left side of a pipe!
    {if (nrow(.) == 0) return(0) else (.) %>%
  dplyr::distinct(s_label) %>%
  dplyr::mutate(pull_n = n()) %>%
  dplyr::distinct(pull_n) %>%
  dplyr::pull(pull_n)
    }

knitr::kable(`duplication in nematode_isolation_s_labeled_plates.csv`, caption =  glue::glue("{n_duplicated_isolations_s_labeled_plates} s_label(s) duplicated in nematode_isolation_s_labeled_plates.csv")) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

#########################################################################
# part 4 find duplication in genotyping google sheet                  ###
#########################################################################
# you will have to find the genotyping sheet specific to this collection trip for this code to work. Paste the PUBLISHED googlesheet URL in gs_key below.
`duplication in genotyping sheet` <- googlesheets::gs_key("17qM6cH9TVAhh7DRQeufHUU5iG5rHCP7cwgEtRA50EkE") %>%
  googlesheets::gs_read("genotyping template", na = c("#N/A", "NA", ""),
                        by = c("s_label")) %>%
  dplyr::filter(!is.na(s_label)) %>%
  # remove c_label variable (this column was hand typed and contains at least 2 errors)
  dplyr::select(s_label, species_id, shipment_number, shipment_sent_date, shipment_received_date, shipment_color, proliferation_48, proliferation_168, proliferating, pcr_product_its2, pcr_product_ssu, notes, manual_blast_notes, ECA_dirty, ECA_clean) %>%
  add_count(s_label) %>%
  dplyr::filter(n > 1)

# find s_labels in genotyping sheet
slabels <- str_subset(`duplication in genotyping sheet`$s_label, pattern = "S-")

# filter genotyping sheet by s_labels matching "S-" pattern
`duplication in genotyping sheet` <- `duplication in genotyping sheet` %>%
  dplyr::filter(s_label %in% slabels)

# get count of duplicated isolations in genotyping sheet
n_duplicated_isolations_genotyping <- `duplication in genotyping sheet` %>%
  #conditional pipe to return NA if dataframe is empty and move on to count s_labels if not empty. Need (.) b/c you can't have . alone on the left side of a pipe!
    {if (nrow(.) == 0) return(0) else (.) %>%
  dplyr::distinct(s_label) %>%
  dplyr::mutate(pull_n = n()) %>%
  dplyr::distinct(pull_n) %>%
  dplyr::pull(pull_n)
    }

knitr::kable(`duplication in genotyping sheet`, caption = glue::glue("{n_duplicated_isolations_genotyping} s_label(s) duplicated in genotyping sheet")) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```
<br> These dataframes are filtered to show the duplications in the raw data from fulcrum or the genotyping sheet. If the dataframe are empty there is no duplication.<br>
**Duplication issue 1:** Duplication in `nematode_field_sampling.csv` for collection_id C-5169.<br>
**Solution:** Remove fulcrum_id `2e161ffe-01ee-45b3-8d28-28db8e070eb7` b/c it does not have an isolation record and it doesn't have substrate temperature or substrate notes.<br>
**Duplication issue 2:** Duplication in `nematode_field_sampling.csv` for collection_id C-5240.<br>
**Solution:** Remove fulcrum_id `9bbdd0cf-6eee-4b9f-a127-11e6039bae00` b/c it does not have an isolation record and was created 1 min before correct record.<br>
**Duplication issue 3:** Duplication in `nematode_field_sampling.csv` for collection_id C-5696.<br>
**Solution:** Remove fulcrum_id `1a822595-a9a4-4319-b57a-7045a3c87efc` b/c it does not have an isolation record and and it doesn't have substrate temperature.<br>
**Duplication issue 4:** Duplication in `nematode_isolation.csv` for collection_id C-5589.<br>
**Solution:** Removed extra isolation record for C-5589, using first isolation record only.<br>
**Duplication issue 5:** Duplication in `nematode_isolation.csv` for collection_id C-5607.<br>
**Solution:** Removed extra isolation record for C-5607, using first isolation record only.<br>
**Duplication issue 6:** Duplication in `nematode_isolation.csv` for collection_id C-5630.<br>
**Solution:** Removed extra isolation record for C-5630, using first isolation record only.<br>

### Location Review
```{r, echo=F, warning = F, message=F}
# Make df for diagnostic plotting
test_df <- fulcrum_dat %>%
  dplyr::filter(!is.na(collection_id)) %>%
  dplyr::distinct(collection_id, .keep_all =T)

# map collection for diagnostic
diagnostic_map <-  map_collection(test_df %>% dplyr::mutate(color = case_when(collection_lat_long_method == "fulcrum" ~ "red",
                                                                              collection_lat_long_method == "photo" ~ "green")), "color")

diagnostic_map
```
Use this map to manually check latitidue and longitude of collection records. Click on the points to get info on the collections.
<br> <font color="darkred">*Red points*</font> are located using `fulcrum` lat,long and may need to be corrected.
<br> <font color="darkgreen">*Green points*</font> are located using `photo` lat,long and are usually accurate.

### C. tribulationis species map
```{r, echo=F, warning = F, message=F}
# Target species map function
#Map_collection function for reviewing collection locations
map_target_species <- function(df, color_use) {

  icos <- iconList(
    red = makeIcon(
      iconUrl = paste0("https://storage.googleapis.com/andersenlab.org/img/red.svg"),
      iconWidth = 15, iconHeight = 15,
      popupAnchorX = 0.001, popupAnchorY = -15,
      iconAnchorX = 15/2, iconAnchorY = 15
    ),
    orange = makeIcon(
      iconUrl = paste0("https://storage.googleapis.com/andersenlab.org/img/orange.svg"),
     iconWidth = 15, iconHeight = 15,
      popupAnchorX = 0.001, popupAnchorY = -15,
      iconAnchorX = 15/2, iconAnchorY = 15
  ),
    blue = makeIcon(
      iconUrl = paste0("https://storage.googleapis.com/andersenlab.org/img/blue.svg"),
      iconWidth = 15, iconHeight = 15,
      popupAnchorX = 0.001, popupAnchorY = -15,
      iconAnchorX = 15/2, iconAnchorY = 15
  )
)
  df <- dplyr::filter(df, !is.na(df[[color_use]])) %>%
    dplyr::mutate(substrate=ifelse(is.na(substrate), "", substrate)) %>%
    dplyr::arrange(species_id)

  #print(df)


  attach(df)
  leaflet::leaflet(data = df, width = "100%", options = list(zoomControl = T)) %>%
    leaflet::addTiles(
      paste0(
        "https://stamen-tiles-{s}.a.ssl.fastly.net/terrain/{z}/{x}/{y}.png",
        jsonlite::read_json("data/thunderforest.json")$key)
    ) %>%
    leaflet::addMarkers(~collection_longitude,
                        ~collection_latitude,
                        popup = glue::glue("<h2>{collection_id}</h2><hr />
                                           <strong>trail:</strong> {collection_trail}<br />
                                           <strong>collection uplaoded by:</strong> {collection_by}<br />
                                           <strong>latitidue, longitude:</strong> {format(round(collection_latitude, 6), nsmall = 6)}, {format(round(collection_longitude, 6), nsmall = 6)}<br />
                                           <strong>location:</strong> {collection_location}<br />
                                           <strong>substrate:</strong> {substrate}<br />
                                           <strong>substrate other:</strong>{substrate_other}<br />
                                           <strong>substrate notes:</strong> {substrate_notes}<br />
                                           <strong>C. tribulationis:</strong> {`C. tribulationis count`}<br /><br />"),
                        popupOptions(maxWidth = 500),
                        icon = icos[ df[[color_use]] ] )

  # temp remove other target species counts
    #<strong>C. elegans:</strong> {`C. elegans count`}<br />
    #<strong>C. briggsae:</strong> {`C. briggsae count`}<br />

  
  #htmlwidgets::saveWidget(m, tempfile(), selfcontained = FALSE)
  #webshot::webshot("temp.html", file = "map.png",
  #        cliprect = "viewport", vwidth = 1000, vheight = 1000)
}

# Make df for diagnostic plotting
target_df <- fulcrum_dat %>%
  dplyr::filter(!is.na(collection_id)) %>%
  dplyr::filter(species_id %in% c("C. tribulationis")) %>% #"C. elegans",  "C. briggsae", 
  dplyr::group_by(collection_id, species_id) %>%
  dplyr::mutate(species_count = n()) %>%
  dplyr::mutate(#`C. elegans count` = ifelse(species_id == "C. elegans", species_count, 0),
                #`C. briggsae count` = ifelse(species_id == "C. briggsae", species_count, 0),
                `C. tribulationis count` = ifelse(species_id == "C. tribulationis", species_count, 0)) %>%
  dplyr::ungroup() %>%
  dplyr::distinct(collection_id, species_id, .keep_all =T) %>%
  dplyr::arrange(collection_id, desc(species_count)) %>%
  dplyr::group_by(collection_id) %>%
  dplyr::mutate(#`C. elegans count` = sum(`C. elegans count`),
                #`C. briggsae count` = sum(`C. briggsae count`),
                `C. tribulationis count` = sum(`C. tribulationis count`)) %>%
  dplyr::ungroup() %>%
  dplyr::distinct(collection_id, .keep_all =T)


# map collection for diagnostic
target_map <-  map_target_species(target_df %>% dplyr::mutate(color = case_when(species_id == "C. elegans" ~ "red",
                                                                                species_id == "C. briggsae" ~ "blue",
                                                                                species_id == "C. tribulationis" ~ "orange")), "color")

target_map
```
Click on the points to get info on the collections.
<br> <font color="darkorange">*Orange points*</font> are C. tribulationis.

### Target species map
```{r, echo=F, warning = F, message=F}
# Target species map function
#Map_collection function for reviewing collection locations
map_target_species <- function(df, color_use) {

  icos <- iconList(
    red = makeIcon(
      iconUrl = paste0("https://storage.googleapis.com/andersenlab.org/img/red.svg"),
      iconWidth = 15, iconHeight = 15,
      popupAnchorX = 0.001, popupAnchorY = -15,
      iconAnchorX = 15/2, iconAnchorY = 15
    ),
    orange = makeIcon(
      iconUrl = paste0("https://storage.googleapis.com/andersenlab.org/img/orange.svg"),
     iconWidth = 15, iconHeight = 15,
      popupAnchorX = 0.001, popupAnchorY = -15,
      iconAnchorX = 15/2, iconAnchorY = 15
  ),
    blue = makeIcon(
      iconUrl = paste0("https://storage.googleapis.com/andersenlab.org/img/blue.svg"),
      iconWidth = 15, iconHeight = 15,
      popupAnchorX = 0.001, popupAnchorY = -15,
      iconAnchorX = 15/2, iconAnchorY = 15
  )
)
  df <- dplyr::filter(df, !is.na(df[[color_use]])) %>%
    dplyr::mutate(substrate=ifelse(is.na(substrate), "", substrate)) %>%
    dplyr::arrange(species_id)

  #print(df)


  attach(df)
  leaflet::leaflet(data = df, width = "100%", options = list(zoomControl = T)) %>%
    leaflet::addTiles(
      paste0(
        "https://stamen-tiles-{s}.a.ssl.fastly.net/terrain/{z}/{x}/{y}.png",
        jsonlite::read_json("data/thunderforest.json")$key)
    ) %>%
    leaflet::addMarkers(~collection_longitude,
                        ~collection_latitude,
                        popup = glue::glue("<h2>{collection_id}</h2><hr />
                                           <strong>trail:</strong> {collection_trail}<br />
                                           <strong>collection uplaoded by:</strong> {collection_by}<br />
                                           <strong>latitidue, longitude:</strong> {format(round(collection_latitude, 6), nsmall = 6)}, {format(round(collection_longitude, 6), nsmall = 6)}<br />
                                           <strong>location:</strong> {collection_location}<br />
                                           <strong>substrate:</strong> {substrate}<br />
                                           <strong>substrate other:</strong>{substrate_other}<br />
                                           <strong>substrate notes:</strong> {substrate_notes}<br />
                                           <strong>C. elegans:</strong> {`C. elegans count`}<br />
                                           <strong>C. briggsae:</strong> {`C. briggsae count`}<br />
                                           <strong>C. tribulationis:</strong> {`C. tribulationis count`}<br /><br />"),
                        popupOptions(maxWidth = 500),
                        icon = icos[ df[[color_use]] ] )
  
  #htmlwidgets::saveWidget(m, tempfile(), selfcontained = FALSE)
  #webshot::webshot("temp.html", file = "map.png",
  #        cliprect = "viewport", vwidth = 1000, vheight = 1000)
}

# Make df for diagnostic plotting
target_df <- fulcrum_dat %>%
  dplyr::filter(!is.na(collection_id)) %>%
  dplyr::filter(species_id %in% c("C. elegans",  "C. briggsae", "C. tribulationis")) %>% 
  dplyr::group_by(collection_id, species_id) %>%
  dplyr::mutate(species_count = n()) %>%
  dplyr::mutate(`C. elegans count` = ifelse(species_id == "C. elegans", species_count, 0),
                `C. briggsae count` = ifelse(species_id == "C. briggsae", species_count, 0),
                `C. tribulationis count` = ifelse(species_id == "C. tribulationis", species_count, 0)) %>%
  dplyr::ungroup() %>%
  dplyr::distinct(collection_id, species_id, .keep_all =T) %>%
  dplyr::arrange(collection_id, desc(species_count)) %>%
  dplyr::group_by(collection_id) %>%
  dplyr::mutate(`C. elegans count` = sum(`C. elegans count`),
                `C. briggsae count` = sum(`C. briggsae count`),
                `C. tribulationis count` = sum(`C. tribulationis count`)) %>%
  dplyr::ungroup() %>%
  dplyr::distinct(collection_id, .keep_all =T)


# map collection for diagnostic
target_map <-  map_target_species(target_df %>% dplyr::mutate(color = case_when(species_id == "C. elegans" ~ "red",
                                                                                species_id == "C. briggsae" ~ "blue",
                                                                                species_id == "C. tribulationis" ~ "orange")), "color")

target_map
```
<font color="darkred">*Red points*</font> are C. elegans.
<br> <font color="darkblue">*Blue points*</font> are C. briggsae.
<br> <font color="darkorange">*Orange points*</font> are C. tribulationis.
<br> Zoom to see all collections and click on the points to get more info.

### Possible new species map
```{r, echo=F, warning = F, message=F}
#Target species map function
#Map_collection function for reviewing collection locations
map_ns <- function(df, color_use) {

  icos <- iconList(
  grey = makeIcon(
      iconUrl = paste0("https://storage.googleapis.com/andersenlab.org/img/grey.svg"),
      iconWidth = 15, iconHeight = 15,
      popupAnchorX = 0.001, popupAnchorY = -15,
      iconAnchorX = 15/2, iconAnchorY = 15
    ),
    orange = makeIcon(
      iconUrl = paste0("https://storage.googleapis.com/andersenlab.org/img/orange.svg"),
     iconWidth = 15, iconHeight = 15,
      popupAnchorX = 0.001, popupAnchorY = -15,
      iconAnchorX = 15/2, iconAnchorY = 15
  ),
    blue = makeIcon(
      iconUrl = paste0("https://storage.googleapis.com/andersenlab.org/img/blue.svg"),
      iconWidth = 15, iconHeight = 15,
      popupAnchorX = 0.001, popupAnchorY = -15,
      iconAnchorX = 15/2, iconAnchorY = 15
  )
)
  df <- dplyr::filter(df, !is.na(df[[color_use]])) %>%
    dplyr::mutate(substrate=ifelse(is.na(substrate), "", substrate)) %>%
    dplyr::arrange(species_id)

  #print(df)


  attach(df)
  leaflet::leaflet(data = df, width = "100%", options = list(zoomControl = T)) %>%
    leaflet::addTiles(
      paste0(
        "https://stamen-tiles-{s}.a.ssl.fastly.net/terrain/{z}/{x}/{y}.png",
        jsonlite::read_json("data/thunderforest.json")$key)
    ) %>%
    leaflet::addMarkers(~collection_longitude,
                        ~collection_latitude,
                        popup = glue::glue("<h2>{collection_id}</h2><hr />
                                           <strong>trail:</strong> {collection_trail}<br />
                                           <strong>collection uplaoded by:</strong> {collection_by}<br />
                                           <strong>latitidue, longitude:</strong> {format(round(collection_latitude, 6), nsmall = 6)}, {format(round(collection_longitude, 6), nsmall = 6)}<br />
                                           <strong>location:</strong> {collection_location}<br />
                                           <strong>substrate:</strong> {substrate}<br />
                                           <strong>substrate other:</strong>{substrate_other}<br />
                                           <strong>substrate notes:</strong> {substrate_notes}<br />
                                           <strong>possible new caeno sp:</strong> {`ns_count`}<br /><br />"),
                        popupOptions(maxWidth = 500),
                        icon = icos[ df[[color_use]] ] )

  #htmlwidgets::saveWidget(m, tempfile(), selfcontained = FALSE)
  #webshot::webshot("temp.html", file = "map.png",
  #        cliprect = "viewport", vwidth = 1000, vheight = 1000)
}

# Make df for diagnostic plotting
ns_df <- fulcrum_dat %>%
  dplyr::filter(possible_new_caeno_sp == 1) %>%
  dplyr::group_by(collection_id) %>%
  dplyr::mutate(ns_count = n()) %>%
  dplyr::ungroup() %>%
  dplyr::distinct(collection_id, .keep_all =T) %>%
  dplyr::arrange(collection_id, desc(ns_count))


# map collection for diagnostic
ns_map <-  map_ns(ns_df %>% dplyr::mutate(color = case_when(possible_new_caeno_sp == 1 ~ "grey",
                                                                                possible_new_caeno_sp == 0 ~ "blue")), "color")

ns_map


```
No possible new Caenorhabditis species identified<br>

### Concerns as of 202000518
**1.** `nematode_isolation_s_labeled_plates.csv` file has 2 records without S-labels. These records are associated with C-5407 and C-5493. They were collected by Matt Rockman and isolated by Claire Buchanan. These might be Matt's isolates that were not proliferating?<br>
**2.** We have three altitude methods, "photo" (exif), "genonames", and "fulcrum". They are prioritized in that order meaning we take "photo" over "genonames" and "geonames" over "fulcrum". Current preference is not very smart and can be improved. For example, when "geonames" method gives altitude of -32768 meters and "fulcrum" method gives 84 meters. Better method selection code should be written.<br>
**3.** There are 4 isntances where S-labels are not found in fulcrum:<br>
S-13381<br>
S-13570<br>
S-13585<br>
S-13657<br>
These are coming from the genotyping Google sheet. S-13570 has a species_id of "C. tribulationis".<br>
**4.** Isolations that need to be resequenced = 9. I don't trust this number because the code is not generalizable across projects. It matches strings containing "redo" in the notes section of the genotyping Google sheet that also have pcr_product_its2 = 1. Unless we standardize notes for what needs to be redone in genotyping Google sheet we can't count on this method to work. From reviewing the genotyping Google sheet it seems like more strains need to be resequenced. Claire will have to verify.<br>
**5.** There is no strain name reporting. This would be helpful in the overall report. Duplications of names and flags for ECA_dirty and ECA_clean not using odd/even numbers correctly.<br>
**6.** There are 12 C-labels with no isolation data. These are:<br>
C-5246<br>
C-5260<br>
C-5389<br>
C-5403<br>
C-5597<br>
C-5620<br>
C-5718<br>
C-5817<br>
C-5818<br>
C-5820<br>
C-5822<br>
C-5962 